Initial Analysis

### 2019-11-07 Initial_Analysis.Rmd
Fixed problem of multiple years of max catch data (e.g. caymans)

Spp <- 600004

@@

  # Get Variables to perform status metric
  Status_Data <- Data %>% 
    anti_join(No_Status_Data, # Removes no status data
              by = c("TaxonKey","Territory")
    ) %>% 
    # Get Max catch and max catch year
    group_by(TaxonKey,Territory) %>% 
    top_n(1,RMean) %>% 
    rename(Max_Peak = RMean,
           Y_Max_Peak = Year) %>% 
    # Get Min catch after peak catch
    left_join(Data,
              by = c("TaxonKey","Territory")
    ) %>% 
    filter(Year > Y_Max_Peak) %>% # Filter years after peak year
    group_by(TaxonKey,Territory) %>% 
    top_n(-1,RMean) %>% # find min value
    group_by(TaxonKey,Y_Max_Peak,Territory,Max_Peak,RMean) %>%  # Solves for years with the same catch data (e.g. Cayman Isl 2013-2014)
    summarise(Year = min(Year)) %>% 
    rename(Post_Max_Min = RMean,
           Y_Post_Max_Min = Year) %>% 
    left_join(Data,
              by = c("TaxonKey","Territory")
    ) %>% 
    # Final Species Status Evaluation 
    mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & ((RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))),"Rebuilding",
                           ifelse((Year < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Year)),"Developing",
                                  ifelse(RMean > (Max_Peak*0.50),"Max Exploited",
                                         ifelse(Year > Y_Max_Peak & ((RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))),"Over Exploited",
                                                ifelse(Year > Y_Max_Peak & RMean < (Max_Peak*0.10),"Collapsed",
                                                       "No Trend")
                                         )
                                  )
                           )
    )
    )

@@

@@

# Number of Transboundary Species
Total_trans_n <- Clean_Results_Trans %>% 
  filter(
    Area_Index >= Min_AI,
    Area_Index <= Max_AI,
    Model_Index >= MI
  )

length(unique(Total_trans_n$TaxonKey)) #633 spp at 100% and 25%

>>>>

Spp <- 601417

@@

  # Get Variables to perform status metric
  Status_Data <- Data %>% 
    # filter(Territory == "Israel (Red Sea)") %>%  # For testing
    anti_join(No_Status_Data, # Removes no status data
              by = c("TaxonKey","Territory")
    ) %>% 
    # Get Max catch and max catch year
    group_by(TaxonKey,Territory) %>% 
    top_n(1,RMean) %>% 
    group_by(TaxonKey,Territory,RMean) %>%  # Solves for years with the same catch data (e.g. Cayman Isl all years)
    summarise(Year = min(Year)) %>%
    rename(Max_Peak = RMean,
           Y_Max_Peak = Year) %>% 
    # Get Min catch after peak catch
    left_join(Data,
              by = c("TaxonKey","Territory")
    ) %>% 
    filter(Year > Y_Max_Peak) %>% # Filter years after peak year
    group_by(TaxonKey,Territory) %>% 
    top_n(-1,RMean) %>% # find min value
    group_by(TaxonKey,Y_Max_Peak,Territory,Max_Peak,RMean) %>%  # Solves for years with the same catch data (e.g. Cayman Isl 2013-2014)
    summarise(Year = min(Year)) %>% 
    rename(Post_Max_Min = RMean,
           Y_Post_Max_Min = Year) %>% 
    left_join(Data,
              by = c("TaxonKey","Territory")
    ) %>% 
    # Final Species Status Evaluation 
    mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & ((RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))),"Rebuilding",
                           ifelse((Year < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Year)),"Developing",
                                  ifelse(RMean > (Max_Peak*0.50),"Max Exploited",
                                         ifelse(Year > Y_Max_Peak & ((RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))),"Over Exploited",
                                                ifelse(Year > Y_Max_Peak & RMean < (Max_Peak*0.10),"Collapsed",
                                                       "No Trend")
                                         )
                                  )
                           )
    )
    )

@@

## Overall results

# Number of Transboundary Species
Total_trans_n <- Clean_Results_Trans %>% 
  filter(
    Area_Index >= Min_AI,
    Area_Index <= Max_AI,
    Model_Index >= MI
  ) %>% 
  pull(TaxonKey) %>% 
  length(unique())

@@
